\subsection{Scalable Verifiable Secret Sharing}
\label{s:scalable-vss}
In this section, we scale $(t,n)$ VSS protocols to large $n$ in the difficult case when $t > n/2$.
Specifically, we reduce \evss's dealing time from $\Theta(nt)$ to \amtDealTime by replacing KZG proofs with AMT proofs.
We call this new VSS protocol \ourvss and describe it below.

\subsubsection{Faster dealing}
\label{s:scalable-vss:overview}
The difference between \ourvss and \evss is very small.
First, players' shares are computed as $s_i = \phi(\omega_N^{i-1})$ (rather than $\phi(i)$ as in \evss), where $N$ is the smallest power of two $\ge n$.
Second, instead of using (slow) KZG proofs, the dealer computes an AMT for $\phi$ at points $\{\omega_N^{i-1}\}_{i\in[n]}$, obtaining the shares $s_i$ for free in the process.
Then, as in \evss, the dealer sends each player $i$ its share $s_i$ but now with an AMT proof $\pi_i$ (see \cref{s:amt:computing-proofs}).
%(i.e., all quotient commitments along $\treepath(i)$ in the AMT of $\phi$).
The verification round, complaint round and reconstruction phase remain the same, except they all use AMT proofs now.

\ourvss's dealing time is \amtDealTime, dominated by the time to compute an AMT.
This is a significant reduction from \evss's $\Theta(nt)$ time, but comes at a small cost due to our larger AMT proofs.
First, the verification round time increases from $\Theta(1)$ to \amtOneShareVerifTime.
Second, the complaint round complexity increases from $O(t)$ to $O(t\log{t})$ time and communication (but we improve it in \cref{s:scalable-vss:batch-complaints}).
Third, the reconstruction phase time increases from $\Theta(t\log^2{t} + n)$ to $O(t\log^2{t} + n\log{t})$  (but we improve it in \cref{s:scalable-vss:reconstruction}).
Finally, the overall communication increases from $\Theta(n)$ to $\amtAllShareVerifTime$.
Nonetheless, in \cref{s:eval:vss}, we show \ourvss's end-to-end time is much smaller than \evss's, which makes these increases justifiable.

\subsubsection{Faster complaints}
\label{s:scalable-vss:batch-complaints}
Kate et al. previously point out that KZG batch proofs (see \cref{s:prelim:polycommit:kzg:batch}) can be used to reduce the communication and the \textit{concrete} computational complexity of \evss's complaint round~\cite{polycommit}.
Suppose $S$ is the set of complaining players.
Without batch proofs, the dealer only has to broadcast $|S|$ previously-computed KZG proofs and each player has to verify them by computing $2|S|$ pairings.
With batch proofs, the dealer spends $\Theta(|S|\log^2{|S|}+t\log{t})$ time to compute the batch proof and each player spends $\Theta(|S|\log^2{|S|}))$ to verify it.
% i.e., because dealer has to interpolate a(x) from its |S| roots and divide \phi(x) of degree t by a(x)
% i.e., because a player has to interpolate a(x) from its |S| roots (i.e., the complaing player IDs) and r(x) from the |S| shares (i.e., r(i)=s_i)

While batch proofs increase asymptotic complexity for the dealer and players, the concrete complexity decreases, since players now only compute two pairings rather than $2|S|$.
% Note: Making a claim about concrete performance of complaint verification without evaluation here.
% Ideally, should have measured the end-to-end time w/ and w/o batch proofs and investigate for which thresholds t batch proofs start making sense.
% After all, the verifiers have to interpolate a polynomial, which could be slower than 2|S| pairings for sufficiently small |S|.
Furthermore, the communication complexity decreases, since only 1 proof rather than $|S|$ needs to be broadcast.
Thus, \ourvss can also use batch proofs and maintain the same performance as \evss during the complaint round.
(However, in \cref{t:vss-comparison}, we do not assume this optimization.)

\subsubsection{Efficient reconstruction}
\label{s:scalable-vss:reconstruction}
In some cases, we can reduce the number of pairings computed during \ourvss's reconstruction phase.
In this phase, the reconstructor is given anywhere from $t$ to $n$ shares and their AMT proofs.
His task is to find a subset of $t$ valid shares and interpolate the secret.
Let us first consider the \textit{best case}, where all submitted shares are \textit{valid}.
In this case, if the reconstructor naively verifies any $t$ AMT proofs, he spends $\Theta(t\log{t})$ time.
But he would be computing the same quotient-accumulator pairings multiple times (as in \cref{eq:amt-verify}), since proofs with intersecting paths will share quotient commitments.
By memoizing these computations, the reconstructor can verify the $t$ proofs in $\Theta(t)$ time.
Alternatively, this can be sped up by exposing a $g^s$ public key during dealing (as in DKG protocols; see \cref{s:scalable-dkg:reconstr}).

Now let us consider the \textit{worst case}, where $n-t$ shares are invalid and $t$ shares are valid.
The reconstructor wants to find the $t$ valid shares as fast as possible.
Once again, he can memoize the quotient-accumulator pairings that are part of successfully validated proofs.
This way, for the $t$ valid proofs, only $\Theta(t)$ pairings need to be computed.
Thus, at most $\Theta((n-t)\log{t})$ pairings could possibly be computed for the invalid proofs.
The worst-case reconstruction time remains $\Theta(n\log{t})$ but, in practice, the number of pairings is reduced significantly by the memoization.
%In practice, the reconstructor might find valid shares earlier and avoid verifying shares whose proof path intersects with valid share proof paths but have different intersecting quotient commitments.

\subsubsection{Public parameters}
\label{s:scalable-vss:public-params}
The \ourvss dealer needs $(t-1)$-SDH public parameters, just like in \evss.
This is because committing to accumulator polynomials of degree $\ge t$ is not necessary, as discussed in \cref{s:amt:public-parameters}.
In fact, adding more public parameters for committing to degree $\ge t$ polynomials would break the \textit{correctness} of \evss and thus of \ourvss~\cite{polycommit}.
Specifically, if the dealer commits to a degree $\ge t$ polynomial $\phi$, then different secrets could be reconstructed, depending on the subset of players whose shares are used.
This is why the $(t-1)$-polyDH assumption (see \cref{d:poly-dh}) is needed in both protocols.
Finally, \ourvss players (and the reconstructor) need $\Theta(\log{t})$ public parameters to verify AMT proofs, an increase from \evss' $\Theta(1)$ (i.e., $g^\tau$).
